### 2022-10-18 AISTATS2023/supplement.tex
started method description
added content in helping material

\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
%\usepackage[accepted]{aistats2022}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

% Supplementary material: To improve readability, you must use a single-column format for the supplementary material.
\onecolumn
\aistatstitle{Instructions for Paper Submissions to AISTATS 2022: \\
Supplementary Materials}

\section{FORMATTING INSTRUCTIONS}

To prepare a supplementary pdf file, we ask the authors to use \texttt{aistats2022.sty} as a style file and to follow the same formatting instructions as in the main paper.
The only difference is that the supplementary material must be in a \emph{single-column} format.
You can use \texttt{supplement.tex} in our starter pack as a starting point, or append the supplementary content to the main paper and split the final PDF into two separate files.

Note that reviewers are under no obligation to examine your supplementary material.

\section{MISSING PROOFS}

The supplementary materials may contain detailed proofs of the results that are missing in the main paper.

\subsection{Proof of Lemma 3}

\textit{In this section, we present the detailed proof of Lemma 3 and then [ ... ]}

\section{ADDITIONAL EXPERIMENTS}

If you have additional experimental results, you may include them in the supplementary materials.

\subsection{The Effect of Regularization Parameter}

\textit{Our algorithm depends on the regularization parameter $\lambda$. Figure 1 below illustrates the effect of this parameter on the performance of our algorithm. As we can see, [ ... ]}

>>>>

\usepackage{aistats2023}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand{\dfdx}{\frac{\partial f}{\partial x_s}}
\newcommand{\xc}{\mathbf{x_c}}
\newcommand{\DY}{\mathbf{\Delta Y}}
\newcommand{\xb}{\mathbf{x}}
\newcommand{\Xcb}{\mathcal{X}_c}
\newcommand{\Xb}{\mathcal{X}}

% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
%\usepackage[accepted]{aistats2022}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

% Supplementary material: To improve readability, you must use a single-column format for the supplementary material.
\onecolumn
\aistatstitle{Instructions for Paper Submissions to AISTATS 2023: \\
Supplementary Materials}

\section{THORETICAL DERIVATIONS}

\subsection{Proof that \(\hat{\sigma}^2(z_1, z_2)\) is an unbiased estimator of \(\sigma_*^2(z_1, z_2)\)}

In Section .. we use that \(\hat{\sigma}^2(z_1, z_2)\) is an unbiased
estimator of
\(\sigma^2_*(z_1, z_2) = \frac{\int_{z_1}^{z_2} \mathbb{E}_{X_c|X_s=z}
  \left [ (f^s(z, X_c) - \mu(z_1, z_2) )^2 \right] \partial z}{z_2 -
  z_1} \), under the assumption that the points are uniformly distributed in \([z_1, z_2)\),
i.e., \(x_s^i \sim \mathcal{U}(z_1, z_2)\).

\paragraph{Proof}

We have made the hypothesis that the points \(\xb^i\) are
coming from the distibution
\(\mathcal{S} = p(X_c|X_s) p(X_s) = p(X_c|X_s) \mathcal{U}(x_s; z_1,
z_2)= \frac{p(\xc|z)}{z_2 - z_1}\) uniformly distributed in the interval \([z_1, z_2)\) in terms

\begin{align}
  \mathbb{E}_\mathcal{S}[\hat{\sigma}^2(z_1, z_2)] &= \mathbb{E}_\mathcal{S}[\frac{1}{|\mathcal{S}|} \sum_{i=1}^{|\mathcal{S}|} (f^s(\xb^i) - \mu(z_1, z_2))^2] \\
  & = \frac{1}{|\mathcal{S}|} \sum_{i=1}^{|\mathcal{S}|} \mathbb{E}_\mathcal{S}[(f^s(\xb^i) - \mu(z_1, z_2))^2]\\
  & = \frac{1}{|\mathcal{S}|} \sum_{i=1}^{|\mathcal{S}|} \mathbb{E}_\mathcal{S}[(f^s(\xb^i) - \mu(z_1, z_2))^2]\\
  \end{align}

\begin{align}
  \sigma^2_*(z_1, z_2) & = \frac{\int_{z_1}^{z_2} \mathbb{E}_{X_c|X_s=z}
  \left [ (f^s(z, X_c) - \mu(z_1, z_2) )^2 \right] \partial z}{z_2 -
                         z_1} \\
  & = \mathbb{E}_{z \sim \mathcal{U}(z_1, z_2)}\mathbb{E}_{X_c|X_s=z}
    \left [ (f^s(z, X_c) - \mu(z_1, z_2) )^2 \right] \\
  & = \mathbb{E}_{X} \left [ (f^s(X) - \mu(z_1, z_2) )^2 \right]
  \end{align}

\subsection{Proof Of Theorem 3.1}

\textit{  If we define (a) the residual \(\rho(z)\) as the difference between
  the expected effect at \(z\) and the bin-effect, i.e
  \(\rho(z) = \mu(z) - \mu(z_1, z_2)\) and (b)
  \(\mathcal{E}(z_1, z_2)\) as the mean squared residual of the bin,
  i.e.
  \(\mathcal{E}(z_1, z_2) = \frac{\int_{z_1}^{z_2}\rho^2(z) \partial
    z}{z_2 - z_1}\), then it holds that:
\begin{equation}
    \label{eq:bin-uncertainty-proof}
 \sigma_*^2(z_1, z_2) = \sigma^2(z_1, z_2) + \mathcal{E}^2(z_1, z_2)
\end{equation}
}

\paragraph{Proof}

\begin{align}
  \sigma_*^2(z_1, z_2) &= \frac{1}{z_2 - z_1}\int_{z_1}^{z_2} \mathbb{E}_{X_c|z} \left [ \left( f^s( z, X_c) - \mu(z_1, z_2) \right)^2 \right] \partial z \\
                       &= \frac{1}{z_2 - z_1} \int_{z_1}^{z_2} \mathbb{E}_{X_c|z} \left [ \left ( f^s(z, X_c) - \mu(z) + \rho(z) \right )^2 \right] \partial z \\
  &= \frac{1}{z_2 - z_1} \int_{z_1}^{z_2} \mathbb{E}_{X_c|z} \left [ (f^s(z, X_c) - \mu(z) )^2 + \rho(z)^2 + 2f^s(z, X_c)\mu(z) ) \right ]\\
  &= \frac{1}{z_2 - z_1} \int_{z_1}^{z_2} \left (
  \underbrace{\mathbb{E}_{X_c|z} \left [ (f^s(z, X_c) - \mu(z) )^2 \right ]}_{\sigma^2(z)}  +
  \underbrace{\mathbb{E}_{X_c|z} \left [ \rho^2(z) \right]}_{\rho^2(z)} +
  2 (\underbrace{\mathbb{E}_{X_c|z} \left [ (f^s(z, X_c)   \right ]}_{\mu(z)} - \mu(z)) \rho(z) )\right )  \partial z \\
  &= \underbrace{\frac{1}{z_2 - z_1} \int_{z_1}^{z_2} \sigma^2(z) \partial z}_{\sigma^2(z_1, z_2)} + \underbrace{\frac{1}{z_2 - z_1} \int_{z_1}^{z_2} \rho^2(z) \partial z}_{\mathcal{E}^2(z_1, z_2)} = \sigma^2(z_1, z_2) + \mathcal{E}^2(z_1, z_2)
\end{align}

\subsection{Proof Of Corollary}

\textit{ If a bin-splitting \(\mathcal{Z}\) minimizes the accumulated error, then it also minimizes
  \(\sum_{k=1}^K\sigma_*^2(z_1, z_2) \Delta z_k \)}

We want to show that

\[ \mathcal{Z}^* = \argmin_{\mathcal{Z}} \sum_{k=1}^K \sigma_*^2(z_{k-1}, z_k) \Delta z_k \Leftrightarrow \mathcal{Z}^* = \argmin_{\mathcal{Z}} \sum_{k=1}^K \mathcal{E}^2(z_{k-1}, z_k) \Delta z_k \]

\paragraph{Proof}

\begin{align}
  \mathcal{Z}^* &= \argmin_{\mathcal{Z}} \sum_{k=1}^K \sigma_*^2(z_{k-1}, z_k) \Delta z_k \\
                & = \argmin_{\mathcal{Z}} \left [ \sum_{k=1}^K (\sigma^2(z_{k-1}, z_k) + \mathcal{E}^2(z_{k-1}, z_k)) \Delta z_k \right ] \\
                & = \argmin_{\mathcal{Z}} \left [ \sum_{k=1}^K \left ( \frac{\Delta z_k}{\Delta z_k} \int_{z_{k-1}}^{z_k} \sigma^2(z) \partial z)   + \mathcal{E}^2(z_{k-1}, z_k) \Delta z_k \right ) \right ] \\
                & = \argmin_{\mathcal{Z}} \left [ \underbrace{\int_{z_0}^{z_K} \sigma^2(z) \partial z}_{\text{independent of } \mathcal{Z}}   + \sum_{k=1}^K\mathcal{E}^2(z_{k-1}, z_k) \Delta z_k) \right ] \\
                & = \argmin_{\mathcal{Z}} \sum_{k=1}^K\mathcal{E}^2(z_{k-1}, z_k) \Delta z_k
  \end{align}

\section{Dynamic Programming}
\label{sec:dynamic-programming}

For achieving a computationally-grounded solution we set a threshold
\(K_{max}\) on the maximum number of bins which also discretizes the
solution space. The width of the bin can take discrete values that are
multiple of the minimum step
\(u = \frac{x_{s, max} - x_{s, min}}{K_{max}}\). For defining the
solution, we use two indexes. The index
\(i \in \{0, \ldots, K_{max}\}\) denotes the point \((z_i)\) and the
index \(j \in \{0, \ldots, K_{max}\} \) denotes the position of the
\(j\)-th multiple of the minimum step, i.e.,
\(x_j = x_{s,min} + j \cdot u\). The recursive cost function
\(T(i,j)\) is the cost of setting \(z_i=x_j\):
\begin{equation}
  \label{eq:recursive_cost}
  \mathcal{T}(i,j) = \mathrm{min}_{l \in \{0, \ldots, K_{max}\}} \left [ \mathcal{T}(i-1, l) + \mathcal{B}(x_l, x_j) \right ]
\end{equation}
%
where \(\mathcal{T}(0,j)\) equals zero if \(j=0\) and \(\infty\) in
any other case. \(\mathcal{B}(x_l, x_j)\) denotes the cost of creating a bin
with limits \([x_l, x_j)]\):

\begin{equation}
  \label{eq:cost_step}
  \mathcal{B}(x_l, x_j) = \begin{cases}
                            \infty, & \text{if $x_j > x_l$ or \(|\mathcal{S}_{(x_j, x_l)}| < N\)}\\
                            0, & \text{if $x_j = x_l$}\\
                            \hat{\sigma}^2(x_j, x_l), &\text{if $x_j \leq x_l$}
  \end{cases}
\end{equation}

The optimal solution is given by solving
\(\mathcal{L} = \mathcal{T}(K_{max}, K_{max})\) and keeping track of the sequence of
steps.

\section{EXPERIMENTS APPEARED AT THE MAIN PAPER}

\subsection{Simulation 1}

\subsection{Simulation 2}

\subsection{Real World Example}

\section{Further Experimentation}

% \section{MISSING PROOFS}

% The supplementary materials may contain detailed proofs of the results that are missing in the main paper.

% % \subsection{Proof of Lemma 3}

% % \textit{In this section, we present the detailed proof of Lemma 3 and then [ ... ]}

% % Given that,

% % The mean effect at a specific point \(x_s\) is:

% % \begin{equation}
% %   \label{eq:3}
% %   \mu(x_s) = \mathbb{E}_{\xc|x_s}\left [\dfdx (x_s, \xc) \right ]
% % \end{equation}

% % The variance at a specific point \(x_s\) is:

% % \begin{equation}
% %   \label{eq:3}
% %   \sigma^2(x_s) = \mathrm{Var}_{\xc|x_s}\left [\dfdx (x_s, \xc) \right ]
% % \end{equation}

% % The mean effect inside the interval \([z_1, z_2)\) is:

% % \begin{equation}
% %   \label{eq:1}
% %   \mu(z_1, z_2) = \frac{1}{z_2-z_1} \int_{z_1}^{z_2} \mathbb{E}_{\xc|x_s}\left [\dfdx (x_s, \xc)\right ]
% % \end{equation}

% % The accumulated variance inside the interval is:

% % \begin{equation}
% %   \label{eq:2}
% %   \sigma^2(z_1, z_2) = \int_{z_1}^{z_2} \mathbb{E}_{\xc|x_s=z} \left [ \left ( \frac{\partial f}{\partial x_s}(x_s, \xc) - \mu(z_1, z_2) \right )^2 \right] \partial z
% % \end{equation}

% % The residual at a specific point \(x_s\) is:

% % \begin{equation}
% %   \label{eq:4}
% %   \rho(x_s) = \mu(x_s) - \mu(z_1, z_2)
% % \end{equation}

% % We want to prove that:

% % \begin{equation}
% %   \label{eq:5}
% %   \sigma^2(z_1, z_2) = \int_{z_1}^{z_2} \sigma^2(z) + \rho^2(z) \partial z
% %   = \int_{z_1}^{z_2} \sigma^2(z) + \int_{z_1}^{z_2} \rho^2(z) \partial z
% % \end{equation}

% % Proof:

% % \begin{gather}
% %   \sigma^2(z_1, z_2) = \int_{z_1}^{z_2} \mathbb{E}_{\xc|x_s=z} \left [ \left( \frac{\partial f}{\partial x_s}( z, \xc) - \mu(z_1, z_2) \right)^2 \right] \partial z \\
% %   = \int_{z_1}^{z_2} \mathbb{E}_{\xc|x_s=z} \left [ \left ( \frac{\partial f}{\partial x_s} - \mu(z) + \rho(z) \right )^2 \right] \partial z \\
% %   = \int_{z_1}^{z_2} \left(
% %   \mathbb{E}_{\xc|x_s=z} \left [ (\frac{\partial f}{\partial x_s} - \mu(z) )^2 \right ]  +
% %   \mathbb{E}_{\xc|x_s=z} \left [ \rho(z)^2 \right] +
% %   \mathbb{E}_{\xc|x_s=z} \left [ 2(\frac{\partial f}{\partial x_s} - \mu(z) )\rho(z) \right ] \right )  \partial z \\
% %   = \int_{z_1}^{z_2}(\sigma^2(z) + \rho^2(z) + 2(\mu(z)-\mu(z))\rho(z))\partial z \\
% %   = \int_{z_1}^{z_2} \sigma^2(z)  + \rho^2(z) \partial z \\
% % \end{gather}

% \section{ADDITIONAL EXPERIMENTS}

% If you have additional experimental results, you may include them in the supplementary materials.

% \subsection{The Effect of Regularization Parameter}

% \textit{Our algorithm depends on the regularization parameter $\lambda$. Figure 1 below illustrates the effect of this parameter on the performance of our algorithm. As we can see, [ ... ]}
